An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2022-03-27 submissions/resubmission-ju-hofmann2/ju-hofmann.Rmd
ready for parallel testing on Windows

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center",
#  cache=TRUE,
  dpi = 144,
  warning = FALSE,
  message = FALSE
)

```

@@

codefigChunkHook <- function(x, options) {
  main <-  defaultChunkHook(x, options)
  before <-
    "\\vspace{1em}
\\begin{adjustbox}{valign=t}
\\begin{minipage}{.39\\textwidth}\n"
  after <-
    paste("\\vspace{1em}
\\end{minipage}
\\begin{minipage}{.59\\textwidth}",
    paste0("\\includegraphics[width=\\textwidth]{ju-hofmann_files/figure-latex/",
                 options[["label"]], "-1.pdf}
\\end{minipage}
\\end{adjustbox}"),
          sep = "\n")
  ## Was a codefig option supplied in chunk header?
  ## If so, wrap code block and graphical output with needed LaTeX code.
  if (!is.null(options$codefig)) {
    main <- gsub("```","", main)
    main <- gsub("=latex","", main)
    main <- paste0("{\\small ", main, "}")
    return(sprintf("%s\n%s\n%s", before, main, after))
  } else {
    return(main)
  }
}

@@

opts_template[["set"]](
codefig = list(codefig = TRUE, fig.show = "hide",
               r.opts = list(width = partWidth),
               tidy.opts = list(width.cutoff = partWidth)))
```

@@

  fullframe <- fullframe %>% mutate(
    land1 = factor(land1, levels = 1:maxland),
    land2 = factor(land2, levels = 1:maxland)
  )
  # get averages, just in case
  matrix <- xtabs(score ~ land1 + land2,
    data = fullframe, addNA = addNA
  ) / xtabs(~land1 + land2, data = fullframe, addNA = addNA)

@@

cmps.result.KM <- extract_feature_cmps(sig1, sig2)
cmps.result.KNM <- extract_feature_cmps(sig1, sig3)
```

@@

    -   **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions. The latter is also called "multi-segment lengths strategy". The parameter \code{npeaks.set} in \code{extract\_feature\_cmps(...)} determines which strategy to use and the number of candidate positions:

        -   If \code{npeaks.set} is an integer vector of length 1, for example \code{npeaks.set = 5}, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
        -   If \code{npeaks.set} is an integer vector of length more than 1, for example \code{npeaks.set = c(5, 3, 1)}, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function. \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks. Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
        -   \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)} computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve. The number of peaks detected is equal to \code{npeaks}, which is an integer. \code{segments}, \code{seg\_outlength}, and \code{nseg} determines the segment in the cross-correlation computation, and \code{comp} gives the reference signature. If the multi-segment lengths strategy is used, then \code{get\_ccr\_peaks(...)} is called in a \code{lapply()} for each level of the basis segment. The resulting list is called \code{ccr.list}.

@@

        -   the function \code{get\_seg\_scale(segments, nseg, out\_length)} is used to obtain the (potentially increased) version of a basis segment. \code{segments}, which is a list containing all basis segments generated by the function \code{get\_segs(...)} in step 1, and \code{nseg} are used to determine the basis segment to be increased. \code{out\_length} specifies the length of the output segment.
        -   \code{get\_ccp(ccr.list, Tx = 25)} tries to identify the "consistent correlation peak". \code{ccr.list} is the result of \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx} determines the size of a tolerance zone used in identifying the consistent correlation peak. \code{get\_ccp(...)} returns \code{NULL} if there is no consistent correlation peak.

3.  **determine the congruent registration position:** A candidate position "receives" votes from basis segments that identify it or a close position within a tolerance zone of \code{Tx} as a candidate position in step 2.
    Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*, indicating that most of the basis segments find their highly similar counterpart in the reference signature in terms of correlation at this registration position.
    In case of ties the middle position is taken as the congruent registration position.
    Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
    The total number of CMPS is the CMPS score of the comparison.
    \code{get\_CMPS(input.ccp, Tx = 25)} is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).

Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks.set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
Here we present it with its default parameters.

```{r, eval=FALSE}
extract_feature_cmps(
  x,
  y,
  seg_length = 50,
  Tx = 25,
  npeaks.set = c(5, 3, 1),
  include = NULL,
  outlength = NULL
)
```

The function \code{extract\_feature\_cmps} allows for the following input from users besides the previously discussed parameters \code{seg\_length}, \code{npeaks.set}, and \code{Tx}:

@@

-   \code{include} determines the format of the function result.
    Besides the \code{CMPS.score}, other aspects of the comparison help in understanding how the \code{CMPS.score} is computed.
    By default \code{include} is set to \code{NULL} and only the \code{CMPS.score} is returned; further results are included when \code{include} is (an abbreviation of) one of or a vector of the following strings: \code{"nseg"}, \code{"congruent.pos"}, \code{"congruent.seg.idx"}, \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}.
    If \code{include} is specified as \code{"full\_result"} (or its abbreviation), the output includes everything listed below.

    -   \code{nseg}: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
    -   \code{congruent.pos}: the congruent registration position;
    -   \code{congruent.seg.idx}: the indices of all congruent matching profile segments;
    -   \code{ccp.list}: a list showing identified candidate positions of all basis segments;
    -   \code{pos.df}: a data frame containing all candidate positions and their respective number of votes;
    -   \code{segments}: a list containing all basis segments;
    -   \code{parameters}: a list containing all input arguments of \code{extract\_feature\_cmps};

@@

```{r sigs, echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row. Signatures in the second row are ordered to be in phase with the signatures above, i.e. matching signatures are displayed on top of each other."}
signatures <- bullets %>% unnest(sigs)
signatures <- signatures %>% mutate(
  bulletland = factor(bulletland, levels=c(paste(rep(c(1,2), each=6), c(1:6,2:6,1), sep="-")))
)
signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
  theme_bw() +
  xlab("Length in mm") +
  ylab("Relative height in micron")
```

@@

# algorithm with multi-peak insepction at three different segment levels
cmps_with_multi_scale <- 
  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                       npeaks.set = c(5,3,1), include = "full_result")

# algorithm with multi-peak inspection at the basis scale only
cmps_without_multi_scale <- 
  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                       npeaks.set = 5, include = "full_result")
```

In the first example, \code{npeaks.set} is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object \code{cmps\_with\_multi\_scale}.
For \code{cmps\_without\_multi\_scale} each basis segment is linked to the top 5 candidate positions.
We use \code{include = "full\_result"} to capture all results.
In this example, the CMPS is 9 when using multiple segments, and 12 when using a single segment.
As discussed in @cmps, using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score based method is walking the line between false positives and false negatives.
As the number of false positives is reduced the number of false negatives might rise.
More discussion and comparisons between the two versions of the CMPS algorithm will be presented in later sections.
Note, that the multi-segment lengths method is slower because the algorithm is run once for each segment length.

@@

comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]), 
                          stringsAsFactors = FALSE)

comparisons <- comparisons %>% 
  left_join(bullets %>% select(bulletland, sig1=sigs),
            by = c("land1" = "bulletland")) %>%
  left_join(bullets %>% select(bulletland, sig2=sigs),
            by = c("land2" = "bulletland"))

@@

comparisons <- comparisons %>% 
  mutate(
    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg),
    cmps_scaled = cmps_score / cmps_nseg
  )

@@

dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
```

@@

```{=tex}
\begin{figure}[hbt]
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot$signature_shift_plot
```
\end{subfigure}
\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
\end{figure}
```
-   Other elements of this list are \code{seg\_shift} and \code{sig\_shift}. \code{sig\_shift} gives the congruent registration position, while \code{seg\_shift} is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.

```{r, echo=TRUE, eval=TRUE}
sig.plot$seg_shift
```

While \code{cmps\_signature\_plot()} focuses on the signature level, \code{cmps\_segment\_plot()} focuses on the segment level.
It provides the "full result" of \code{extract\_feature\_cmps()}, but also takes an argument, \code{seg.idx}, indicating which segment should be inspected.
When checking \code{sig.plot\$seg\_shift} we notice that segment number 6 is not one of the congruent matching profile segments.
We can therefore set \code{seg.idx = 6} in \code{cmps\_segment\_plot()} and investigate the reason why this segment disagrees with the congruent registration position.

@@

-   \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6 at level one (in its original length). We used \code{npeaks.set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when calculating the CMPS score. Therefore the top five peaks are identified in the cross-correlation curve at level one. Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the \code{segment\_plot}. The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
-   \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment 6 at level one. It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6. The five highest peaks are marked by dots on the curve.

```{=tex}
\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at level one. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, 
  seg.idx = 6
)
seg.plot[[1]]$segment_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot[[1]]$scale_ccf_plot
```
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}
```
Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the \code{segment\_plot} and \code{scale\_ccf\_plot} of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of \code{ggpubr::ggarrange()}.

@@

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
```
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together. We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1). The highest peak position at level three is marked by the green dashed line across all segment levels. However, the highest peak on level three does not coincide with any of the top five highest peaks at level one. This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
\end{figure}
```
In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
We can see that the basis segment 6 does obtain a peak near the congruent registration position at level two and level three, respectively; however, this position doesn't give one of the five highest peaks at level one.
As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi-segment lengths strategy.
The identified top five peaks at level one are also examples of "false positive" peaks.
The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.

@@

```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets. Land engraving pairs generated by the same land (KM comparisons) are highlighted. Note that in this example the axis along Bullet 2 starts with Land 2. This corresponds to Phase 1 in equation (1).", out.width=".7\\textwidth", fig.align="center"}
dframe <- dframe %>% mutate(
  landA = paste0("L", landA),
  landB = paste0("L", landB),
  landB = factor(landB, levels = paste0("L", c(2:6,1))),
  bulletA = paste0("Bullet ", bulletA),
  bulletB = paste0("Bullet ", bulletB)
)

dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
  geom_tile() + 
  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
  scale_colour_manual("Source", values="darkorange") +
  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
  ylab("Bullet2 Lands") + 
  geom_text(aes(label=cmps_score)) +
  theme_bw() +
  theme(aspect.ratio = 1)
```

@@

```{r tiles2, echo=FALSE, fig.cap="Plot (a) shows the highest possible CMPS scores (the total number of basis segments) for the 36 comparisons. (b) shows the scaled CMPS scores for the 36 comparisons.", out.width=".7\\textwidth", fig.align="center"}
p1 <- dframe %>% ggplot(aes(x = landA, y = landB)) + 
  geom_tile(fill = "grey") + 
  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
  scale_colour_manual("Source", values="darkorange") +
  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
  ylab("Bullet2 Lands") + 
  geom_text(aes(label=cmps_nseg)) +
  theme_bw() +
  theme(aspect.ratio = 1)

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center",
  #  cache=TRUE,
  dpi = 144,
  warning = FALSE,
  message = FALSE
)
```

@@

codefigChunkHook <- function(x, options) {
  main <- defaultChunkHook(x, options)
  before <-
    "\\vspace{1em}
\\begin{adjustbox}{valign=t}
\\begin{minipage}{.39\\textwidth}\n"
  after <-
    paste("\\vspace{1em}
\\end{minipage}
\\begin{minipage}{.59\\textwidth}",
      paste0(
        "\\includegraphics[width=\\textwidth]{ju-hofmann_files/figure-latex/",
        options[["label"]], "-1.pdf}
\\end{minipage}
\\end{adjustbox}"
      ),
      sep = "\n"
    )
  ## Was a codefig option supplied in chunk header?
  ## If so, wrap code block and graphical output with needed LaTeX code.
  if (!is.null(options$codefig)) {
    main <- gsub("```", "", main)
    main <- gsub("=latex", "", main)
    main <- paste0("{\\small ", main, "}")
    return(sprintf("%s\n%s\n%s", before, main, after))
  } else {
    return(main)
  }
}

@@

opts_template[["set"]](
  codefig = list(
    codefig = TRUE, fig.show = "hide",
    r.opts = list(width = partWidth),
    tidy.opts = list(width.cutoff = partWidth)
))
```

@@

  fullframe <- fullframe %>% mutate(
    land1 = factor(land1, levels = 1:maxland),
    land2 = factor(land2, levels = 1:maxland)
  )
  # get averages, just in case
  matrix <- xtabs(score ~ land1 + land2,
    data = fullframe, addNA = addNA
  ) / xtabs(~ land1 + land2, data = fullframe, addNA = addNA)

@@

cmps_result_KM <- extract_feature_cmps(sig1, sig2)
cmps_result_KNM <- extract_feature_cmps(sig1, sig3)
```

@@

    -   **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions. The latter is also called "multi-segment lengths strategy". The parameter \code{npeaks\_set} in \code{extract\_feature\_cmps(...)} determines which strategy to use and the number of candidate positions:

        -   If \code{npeaks\_set} is an integer vector of length 1, for example \code{npeaks\_set = 5}, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
        -   If \code{npeaks\_set} is an integer vector of length more than 1, for example \code{npeaks\_set = c(5, 3, 1)}, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function. \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks. Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
        -   \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)} computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve. The number of peaks detected is equal to \code{npeaks}, which is an integer. \code{segments}, \code{seg\_outlength}, and \code{nseg} determines the segment in the cross-correlation computation, and \code{comp} gives the reference signature. If the multi-segment lengths strategy is used, then \code{get\_ccr\_peaks(...)} is called in a \code{lapply()} for each level of the basis segment. The resulting list is called \code{ccr\_list}.

@@

        -   the function \code{get\_seg\_scale(segments, nseg, out\_length)} is used to obtain the (potentially increased) version of a basis segment. \code{segments}, which is a list containing all basis segments generated by the function \code{get\_segs(...)} in step 1, and \code{nseg} are used to determine the basis segment to be increased. \code{out\_length} specifies the length of the output segment.
        -   \code{get\_ccp(ccr\_list, Tx = 25)} tries to identify the "consistent correlation peak". \code{ccr\_list} is the result of \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx} determines the size of a tolerance zone used in identifying the consistent correlation peak. \code{get\_ccp(...)} returns \code{NULL} if there is no consistent correlation peak.

3.  **determine the congruent registration position:** A candidate position "receives" votes from basis segments that identify it or a close position within a tolerance zone of \code{Tx} as a candidate position in step 2.
    Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*, indicating that most of the basis segments find their highly similar counterpart in the reference signature in terms of correlation at this registration position.
    In case of ties the middle position is taken as the congruent registration position.
    Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
    The total number of CMPS is the CMPS score of the comparison.
    \code{get\_CMPS(input\_ccp, Tx = 25)} is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).

Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
Here we present it with its default parameters.

```{r, eval=FALSE}
extract_feature_cmps(
  x,
  y,
  seg_length = 50,
  Tx = 25,
  npeaks_set = c(5, 3, 1),
  include = NULL,
  outlength = NULL
)
```

The function \code{extract\_feature\_cmps} allows for the following input from users besides the previously discussed parameters \code{seg\_length}, \code{npeaks\_set}, and \code{Tx}:

@@

-   \code{include} determines the format of the function result.
    Besides the \code{CMPS\_score}, other aspects of the comparison help in understanding how the \code{CMPS\_score} is computed.
    By default \code{include} is set to \code{NULL} and only the \code{CMPS\_score} is returned; further results are included when \code{include} is (an abbreviation of) one of or a vector of the following strings: \code{"nseg"}, \code{"congruent\_pos"}, \code{"congruent\_seg\_idx"}, \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}.
    If \code{include} is specified as \code{"full\_result"} (or its abbreviation), the output includes everything listed below.

    -   \code{nseg}: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
    -   \code{congruent\_pos}: the congruent registration position;
    -   \code{congruent\_seg\_idx}: the indices of all congruent matching profile segments;
    -   \code{ccp\_list}: a list showing identified candidate positions of all basis segments;
    -   \code{pos\_df}: a data frame containing all candidate positions and their respective number of votes;
    -   \code{segments}: a list containing all basis segments;
    -   \code{parameters}: a list containing all input arguments of \code{extract\_feature\_cmps};

@@

```{r sigs, echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row. Signatures in the second row are ordered to be in phase with the signatures above, i.e. matching signatures are displayed on top of each other."}
signatures <- bullets %>% unnest(sigs)
signatures <- signatures %>% mutate(
  bulletland = factor(bulletland, levels = c(paste(rep(c(1, 2), each = 6), c(1:6, 2:6, 1), sep = "-")))
)
signatures %>% ggplot(aes(x = x / 1000, y = sig)) +
  geom_line() +
  facet_wrap(~bulletland, ncol = 6) +
  theme_bw() +
  xlab("Length in mm") +
  ylab("Relative height in micron")
```

@@

# algorithm with multi-peak insepction at three different segment levels
cmps_with_multi_scale <-
  extract_feature_cmps(sigs1$sig, sigs2$sig,
    npeaks_set = c(5, 3, 1), include = "full_result"
  )

# algorithm with multi-peak inspection at the basis scale only
cmps_without_multi_scale <-
  extract_feature_cmps(sigs1$sig, sigs2$sig,
    npeaks_set = 5, include = "full_result"
  )
```

In the first example, \code{npeaks\_set} is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object \code{cmps\_with\_multi\_scale}.
For \code{cmps\_without\_multi\_scale} each basis segment is linked to the top 5 candidate positions.
We use \code{include = "full\_result"} to capture all results.
In this example, the CMPS is 9 when using multiple segments, and 12 when using a single segment.
As discussed in @cmps, using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score based method is walking the line between false positives and false negatives.
As the number of false positives is reduced the number of false negatives might rise.
More discussion and comparisons between the two versions of the CMPS algorithm will be presented in later sections.
Note, that the multi-segment lengths method is slower because the algorithm is run once for each segment length.

@@

comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]),
  stringsAsFactors = FALSE
)

comparisons <- comparisons %>%
  left_join(bullets %>% select(bulletland, sig1 = sigs),
    by = c("land1" = "bulletland")
  ) %>%
  left_join(bullets %>% select(bulletland, sig2 = sigs),
    by = c("land2" = "bulletland")
  )

@@

comparisons <- comparisons %>%
  mutate(
    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS_score),
    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg),
    cmps_scaled = cmps_score / cmps_nseg
  )

@@

dframe$samesource <- with(dframe, bullet_to_land_predict(land1 = landA, land2 = landB, cmps_score, difference = 1))
```

@@

```{=tex}
\begin{figure}[hbt]
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig_plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig_plot$segment_shift_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig_plot$signature_shift_plot
```
\end{subfigure}
\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
\end{figure}
```
-   Other elements of this list are \code{seg\_shift} and \code{sig\_shift}. \code{sig\_shift} gives the congruent registration position, while \code{seg\_shift} is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.

```{r, echo=TRUE, eval=TRUE}
sig_plot$seg_shift
```

While \code{cmps\_signature\_plot()} focuses on the signature level, \code{cmps\_segment\_plot()} focuses on the segment level.
It provides the "full result" of \code{extract\_feature\_cmps()}, but also takes an argument, \code{seg\_idx}, indicating which segment should be inspected.
When checking \code{sig\_plot\$seg\_shift} we notice that segment number 6 is not one of the congruent matching profile segments.
We can therefore set \code{seg\_idx = 6} in \code{cmps\_segment\_plot()} and investigate the reason why this segment disagrees with the congruent registration position.

@@

-   \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6 at level one (in its original length). We used \code{npeaks\_set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when calculating the CMPS score. Therefore the top five peaks are identified in the cross-correlation curve at level one. Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the \code{segment\_plot}. The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
-   \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment 6 at level one. It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6. The five highest peaks are marked by dots on the curve.

```{=tex}
\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at level one. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg_plot <- cmps_segment_plot(
  cmps_with_multi_scale,
  seg_idx = 6
)
seg_plot[[1]]$segment_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg_plot[[1]]$scale_ccf_plot
```
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}
```
Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the \code{segment\_plot} and \code{scale\_ccf\_plot} of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of \code{ggpubr::ggarrange()}.

@@

ggarrange(
  plotlist =
    unlist(seg_plot,
      recursive = FALSE
    ),
  ncol = 2,
  nrow = 3
)
```
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together. We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1). The highest peak position at level three is marked by the green dashed line across all segment levels. However, the highest peak on level three does not coincide with any of the top five highest peaks at level one. This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
\end{figure}
```
In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
We can see that the basis segment 6 does obtain a peak near the congruent registration position at level two and level three, respectively; however, this position doesn't give one of the five highest peaks at level one.
As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi-segment lengths strategy.
The identified top five peaks at level one are also examples of "false positive" peaks.
The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.

@@

```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets. Land engraving pairs generated by the same land (KM comparisons) are highlighted. Note that in this example the axis along Bullet 2 starts with Land 2. This corresponds to Phase 1 in equation (1).", out.width=".7\\textwidth", fig.align="center"}
dframe <- dframe %>% mutate(
  landA = paste0("L", landA),
  landB = paste0("L", landB),
  landB = factor(landB, levels = paste0("L", c(2:6, 1))),
  bulletA = paste0("Bullet ", bulletA),
  bulletB = paste0("Bullet ", bulletB)
)

dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) +
  geom_tile() +
  geom_tile(aes(colour = "same land"), fill = NA, data = dframe %>% filter(samesource), size = 1) +
  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) +
  scale_colour_manual("Source", values = "darkorange") +
  facet_grid(bulletB ~ bulletA) +
  xlab("Bullet1 Lands") +
  ylab("Bullet2 Lands") +
  geom_text(aes(label = cmps_score)) +
  theme_bw() +
  theme(aspect.ratio = 1)
```

@@

```{r tiles2, echo=FALSE, fig.cap="Plot (a) shows the highest possible CMPS scores (the total number of basis segments) for the 36 comparisons. (b) shows the scaled CMPS scores for the 36 comparisons.", out.width=".7\\textwidth", fig.align="center"}
p1 <- dframe %>% ggplot(aes(x = landA, y = landB)) +
  geom_tile(fill = "grey") +
  geom_tile(aes(colour = "same land"), fill = NA, data = dframe %>% filter(samesource), size = 1) +
  scale_colour_manual("Source", values = "darkorange") +
  facet_grid(bulletB ~ bulletA) +
  xlab("Bullet1 Lands") +
  ylab("Bullet2 Lands") +
  geom_text(aes(label = cmps_nseg)) +
  theme_bw() +
  theme(aspect.ratio = 1)

p2 <- dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_scaled)) +
  geom_tile() +
  geom_tile(aes(colour = "same land"), fill = NA, data = dframe %>% filter(samesource), size = 1) +
  scale_fill_gradient2("Scaled CMPS", low = "gray80", high = "darkorange", midpoint = 0.3) +
  scale_colour_manual("Source", values = "darkorange") +
  facet_grid(bulletB ~ bulletA) +
  xlab("Bullet1 Lands") +
  ylab("Bullet2 Lands") +
  geom_text(aes(label = round(cmps_scaled, 2))) +
  theme_bw() +
  theme(aspect.ratio = 1)

ggarrange(p1, p2,
  common.legend = TRUE, legend = "bottom", labels = c("(a)", "(b)")
)
```
